---
title: "Demo_Adjustement"
author: "CDV"
date: "04 janvier 2016"
output: html_document
---


```{r, package}

library(ggplot2)
library(gridExtra)
library(car)
library(effects)
```


## Data simulation
```{r, data}
set.seed(12)
Smoke<-seq(0,50, length.out=100) 
a1=80
b1=-1.5
RespCap<- a1 + b1 *Smoke+rnorm(100,20,10)

Mint<-Smoke/2+15+rnorm(100,10,14)
mydata<-data.frame(RespCap,Mint,Smoke)
#head(mydata[,1:2])

```




## Exploring Mint and Respiratory capacities relationship
```{r mod 1, echo=TRUE}
# display data
head(mydata[,1:2])

# plot Respiratory capacities vs Mint
ggplot(mydata, aes(x=Mint,y=RespCap))+
  geom_point(size=4)

# resgression
mod1<-lm(RespCap~Mint, data=mydata)


summary(mod1)
par(mfrow=c(2,2))
plot(mod1)

# plot Respiratory capacities vs Mint
xmin<-min(mydata$Mint)
xmax<-max(mydata$Mint)
predicted<-data.frame(Mint=seq(xmin,xmax, length.out=100))
predicted$Mint<-predict(mod1,predicted)

ggplot(mydata, aes(x=Mint,y=RespCap))+
  geom_point(size=4)+
  geom_smooth(method="lm")


plot(allEffects(mod1))
```


Mint has a significant negative effect on respiratory capacities.

## Exploring Mint and Respiratory capacities relationship taking in acount Smoke
```{r mod 2, echo=TRUE, message=FALSE, warning=FALSE}
# display data
head(mydata)

# plot Respiratory capacities vs Mint
ggplot(mydata, aes(x=Mint,y=RespCap, fill=Smoke))+
  geom_point(size=4, shape=21)+
  scale_fill_gradient2(low="green", mid="yellow",high="red", midpoint=25)

# check for multicollinearity
with(mydata, cor(Mint,Smoke))

# resgression
mod2<-lm(RespCap~Mint+Smoke, data=mydata)
vif(mod2)

summary(mod2)
par(mfrow=c(2,2))
plot(mod2)

plot(allEffects(mod2))

```

Mint has no more a significant effect.
So the effect we saw was caused by Smoke and the correlation between Smoke and Mint.



## Exploring Smoke and Respiratory capacities 
```{r mod 3, echo=FALSE}

# plot Respiratory capacities vs Mint
ggplot(mydata, aes(x=Smoke,y=RespCap))+
  geom_point(size=4)+
  geom_smooth(method="lm")

# resgression
mod3<-lm(RespCap~Smoke, data=mydata)

summary(mod3)
par(mfrow=c(2,2))
plot(mod3)
```

Smoke has a very significant negative impact on Respiratory capacities !


